---
title: "simpleRegress"
author: "Cyndhell Anne Pilarca"
date: "Summer 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model LENGTH ~ NECK  this is an example  

We are to compute regression models finding one regression model that does the best job in predicting the bear length and its corresponded to the bear neck size, age , hand, with and head length.

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

The adjusted r-square that is the largest is the best. The neck size of adjusted r-square is about 0.7476


## Compare all models that predict LENGTH other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 


```{r}
simp <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simp)
summary.lm(simp)
```

The adjusted R-squared for head length is 0.8483.

```{r}
simp <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(simp)
summary.lm(simp)
```

The adjusted r-studio for the head width is 0.5321.


```{r}
simp <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(simp)
summary.lm(simp)
```

The adjusted r-square for age is 0.5073.

```{r}
simp <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simp)
summary.lm(simp)
```

The adjusted r-square for chest is 0.7869.

```{r}
simp <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simp)
summary.lm(simp)
```

The adjusted r-square for weight is 0.7423.

# Conclusion
To restate the question we need to compute regression models finding one regression model that does the best job in predicting the bear length and its corresponded to the bear neck size, age, hand, with and head length. In Conclusion based on the data we gathered the head length (0.8483) is the best because it have the largest number. The second best is the Chest (0.7869). The third is the neck which is (0.7476). Continuity, the weight (0.7423) next is head weight (0.5321), lastly the age (0.5073).





